Appendix C: Building Environments for Deep Reinforcement Learning

### 2021-06-11 appendices/appendix-C-environments.Rmd
Small edits on appendix C

a observation function (sometimes called the 'emission' function, $E$) giving the observed state as a function of the current state and possibly also the action (i.e. different actions could potentially influence the accuracy of the observation):

@@

In practice, an environment may include additional logic for rendering information about it's current states as output.
Effective environments may often work in a transformed variable space, for example, `gym_fishing` maps the space $[0,2K]$ into the space $[-1, 1]$, which significantly improves the performance. 
Other features, such as 32 bit precision numeric values for state and action spaces, can improve the performance of the environment on GPU-based computation.

>>>>

an observation function (sometimes called the 'emission' function, $E$) giving the observed state as a function of the current state and possibly also the action (i.e. different actions could potentially influence the accuracy of the observation):

@@

In practice, an environment may include additional logic for rendering information about it's current states as output.
Effective environments may often work in a transformed variable space, for example, `gym_fishing` maps the space $[0,2K]$ into the space $[-1, 1]$, which significantly improves agent performance. 
Other features, such as 32 bit precision numeric values for state and action spaces, can also improve agent performance with GPU-based computation.
